### 2016-11-04 Paper_v1.tex
Nov4

\begin{figure}[ht]
\centering
\includegraphics[width=0.94\textwidth]{./Figures/SensAll.png}
\caption{Mean and standard error of local sensitivities of rate constants (top), saturation constants (middle), and control parameters (bottom).}
\label{fig:LocalSensitivity}
\end{figure}

\begin{figure}[ht]
\centering
%\includegraphics[width=1.00\textwidth]{./Figures/SensitivitiesHalfTall.pdf}
\includegraphics[width=1.00\textwidth]{./Figures/Sensitivity.pdf}
\includegraphics[width=1.00\textwidth]{./Figures/Metab_sensitivity.pdf}
\caption{Total-order global sensitivities for experimentally controllable initial conditions, including glucose, oxygen, amino acids, and enzymes.}
\label{fig:GlobalSensitivity}
\end{figure}

@@

\begin{figure}[ht]
\centering
\includegraphics[width=1.00\textwidth]{./Figures/C_Secretion.pdf}
\caption{Total-order global sensitivities of protein export flux to glutamic acid, oxygen and glucose import flux upper bounds, and translation initiation rate upper bound. Lactate, ethanol, acetate, and formate export fluxes were held constant at 0.1 mM/hr in the control case. One of these export fluxes was held constant at 10 mM/hr, while the others were held constant at 0.1 mM/hr, in each of the other four cases.}
\label{fig:C_Secretion.pdf.pdf}
\end{figure}

>>>>

%\begin{table}[ht]
%\centering
%\includegraphics[width=0.94\textwidth]{./Figures/AIC.pdf}
%\caption{}
%\label{fig:AIC}
%\end{table}

\begin{figure}[ht]
\centering
\includegraphics[width=0.94\textwidth]{./Figures/ClusterCAT.pdf}
\caption{Normalized first-order and pairwise sensitivities of CAT production to rate constants. Dark pixels indicate the most sensitive indices. Dendrogram indicates high responders (dark gray background), medium responders (medium gray background), and low responders (light gray background).}
\label{fig:ClusterCAT}
\end{figure}

\begin{figure}[ht]
\centering
\includegraphics[width=1.00\textwidth]{./Figures/ClusterSystem.pdf}
\caption{Normalized first-order and pairwise sensitivities of system state to rate constants. Dark pixels indicate the most sensitive indices. Dendrogram indicates high responders (dark gray background), medium responders (medium gray background), and low responders (light gray background).}
\label{fig:ClusterSystem}
\end{figure}

@@

\begin{figure}[ht]
\centering
\includegraphics[width=1.00\textwidth]{./Figures/C_Secretion.pdf}
\caption{Total-order global sensitivities of protein export flux to glutamic acid, oxygen and glucose import flux upper bounds, and translation initiation rate upper bound. Lactate, ethanol, acetate, and formate export fluxes were held constant at 0.1 mM/hr in the control case. One of these export fluxes was held constant at 10 mM/hr, while the others were held constant at 0.1 mM/hr, in each of the other four cases.}
\label{fig:C_Secretion.pdf}
\end{figure}

%\begin{figure}[ht]
%\centering
%\includegraphics[width=1.00\textwidth]{./Figures/MikeYield.pdf}
%\caption{}
%\label{fig:MikeYield.pdf}
%\end{figure}
